Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-20 ba_resubmit/rebuttal/response.tex

\setcounter{responsectr}{0}
\section{Reviewer Comments}

	\pointRaised{R}{%
	For the missing data treatment now included just before Section 2.1, is the assumption truly missing at random, or missing completely at random? Or, does this distinction not matter because of the independence assumed across elements of the comparison vector?}

	\reply{\textcolor{teal}{The distinction does not matter due to assuming that the comparison vectors are conditionally independent given the coreference matrix (or matching label). We now state the following in Section 3, page 5:}

	\textcolor{teal}{In many record linkage tasks, the records in $A$ or $B$ have missing fields, so that some $\gamma_{ij}^f$ could be missing.  To handle this, we follow the approach described in \cite{sadinle_bayesian_2017}.  Let $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. We assume that any missing comparisons are missing at random (MAR) or missing completely at random (MCAR). For likelihood based inference, both MAR and MCAR lead to ignorability, or rather, being able to consider the likelihood for the observed data \citep[Section 6.2]{LittleRubin2002}, so that we can marginalize over the missing data and perform all computation using the observed data \citep{sadinle_detecting_2014, sadinle_bayesian_2017}.}

%	\textcolor{teal}{``\textcolor{teal}{We now explain how we accommodate missing fields, which leads to missing comparison vectors. To denote a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. Assume the comparison vectors are conditionally independent given the coreference matrix (or matching label) and that missing comparisons are missing at random (MAR) or missing completely at random (MCAR). It is important to note that for likelihood based inference, both MAR and MCAR lead to ignorability, or rather, being able to consider the likelihood for the observed data \citep[Section 6.2]{LittleRubin2002}. Therefore, we can marginalize over the missing data and perform all computation using the observed data, leading to (6a). For further details on these connections, refer to \cite[Section 6.2]{LittleRubin2002}, \cite[Section 3.1]{sadinle_detecting_2014}, and \citep[Section 4.2]{sadinle_bayesian_2017}}."}
	}

### 2023-07-20 ba_resubmit/kundinger_final.tex
update.
update R.0.

	\textcolor{red}{Suggestion: Chunk is award. Perhaps partition/block/batch/segment. I might like segment since partition/block have meanings in record linkage already. }

@@

	\begin{figure}[t]
		\begin{center}
		\includegraphics[width=0.7\textwidth]{finalFigures/figures/sadinle_speed_plot2} 
	% \includegraphics[width=0.7\textwidth]{../notes/figures/sadinle_speed_plot2} 
			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations, including the hashing step for \texttt{fabl}, for increasing values of both $n_A$ and $n_B$, as described in Section \ref{speed}. We see near quadratic growth in run-time for \texttt{BRL}, and near linear growth for \texttt{fabl}.}\label{fig:speed1}
		\end{center}
	\end{figure}

@@

	\begin{figure}[h!]
		\begin{center} 
		\includegraphics[width=0.7\textwidth]{finalFigures/figures/speed_plot_fixed_nB_slides} 
	%	\includegraphics[width=0.7\textwidth]{../notes/figures/speed_plot_fixed_nB_slides} 
			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations, including hashing step for \texttt{fabl}, with $n_B$ fixed at 500, as described in Section \ref{speed}. We see near linear growth in run-time for \texttt{BRL}, and near constant run-time for \texttt{fabl}.}\label{fig:speed2}
		\end{center}
	\end{figure}

@@

	\begin{figure}[t]
		\begin{center}
		\includegraphics[width=0.7\textwidth]{finalFigures/figures/sadinle_sim_plot2} 
			%\includegraphics[width=0.7\textwidth]{../notes/figures/sadinle_sim_plot2} 
			\caption{Posterior means and credible intervals for accuracy metrics under the replication of simulation study from \cite{sadinle_bayesian_2017}. For each level of overlap and each level of error, we have 100 paired sets of 500 records. Thus this table summarizes results for 900 data files. We see comparable performance for all levels of error and overlap.}
			\label{fig:sadinle_simulation}
		\end{center}
	\end{figure}

@@

\begin{figure}
	\begin{minipage}[c]{0.4\linewidth}
		\begin{center}
		\includegraphics[width=\linewidth]{finalFigures/SEI_sensitivity/Z_plot}
%		\includegraphics[width=\linewidth]{../SEI_sensitivity/Z_plot}
		\caption{Distinct values of $\hat{Z}$ in Section \ref{SEI-sensitivity} simulation.}
		\label{fig:SEI_Z}
		\end{center}
	\end{minipage}
	\hfill
	\begin{minipage}[c]{0.5\linewidth}
		\begin{center}
		\includegraphics[width=\linewidth]{finalFigures/SEI_sensitivity/eval_plot} 
%	\includegraphics[width=\linewidth]{../SEI_sensitivity/eval_plot} 
		\caption{Means and 95\% credible intervals for recall and precision in Section \ref{SEI-sensitivity} simulation.}
		\label{fig:SEI_eval}
	\end{center}
	\end{minipage}%
\end{figure}
	\section{Case Studies}
	\label{sec:case-studies}

@@

	\begin{figure}[t]
		\begin{center}
		         \includegraphics[width=0.6\textwidth]{finalFigures/el_salvador/overlap_distribution_smallP_bayes}
%			\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/overlap_distribution_smallP_bayes}
			\caption{Posterior distribution and Bayes estimate of overlap across the two files. We note they are quite similar under both methods.}
			\label{fig:overlap-plot}
		\end{center}
	\end{figure}

	\begin{figure}[t]
		\begin{center}
		         \includegraphics[width=0.6\textwidth]{finalFigures/el_salvador/m_posterior_smallP} 
%			\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/m_posterior_smallP} 
			\caption{Posterior estimates of $\bm{m}$ parameters with 95\% credible intervals for the El Salvador case study. They are quite similar across the two methods.}\label{fig:m-and-u}
			\label{fig:m-and-u}
		\end{center}
	\end{figure}

@@

	\begin{figure}[h]
		\begin{center}
		        \includegraphics[width=0.6\textwidth]{finalFigures/nltcs/overlap_posterior4}
%			\includegraphics[width=0.6\textwidth]{../notes/figures/nltcs/overlap_posterior4}
			\caption{Posterior distribution and Bayes estimate of overlap across years 1982 and 1989 of NLTCS data.}
			\label{fig:nltcs-overlap-plot}
		\end{center}
	\end{figure}

@@

\begin{figure}[t]
	\begin{center}
	        \includegraphics[width=0.6\textwidth]{finalFigures/figures/sadinle_sim_plot_partial_DR} 
		%\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot_partial_DR} 
		\caption{Negative predictive value (NPV), positive predictive value (PPV), and decision rate (DR) on data files in the simulation in Appendix \ref{partial}. We see poorer performance for \texttt{fabl} only in situations with high overlap.}
		\label{fig:sadinle_simulation_partial}
	\end{center}
\end{figure}

@@

	\begin{figure}[!h]
		\begin{center}
		        \includegraphics[width=0.6\textwidth]{finalFigures/figures/sim_overlap_trace} 
%			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_overlap_trace} 
			\caption{Representative traceplot of overlap between files from simulation study in Section \ref{accuracy}.}\label{fig:sim_overlap_trace}
		\end{center}
	\end{figure}

	\begin{figure}[!h]
		\begin{center}
		         \includegraphics[width=0.6\textwidth]{finalFigures/figures/sim_m_trace} 
%			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_m_trace} 
			\caption{Representative traceplot of $\bm{m}$ parameter from simulation study in Section \ref{accuracy}.}\label{fig:sim_m_trace}
		\end{center}
	\end{figure}

	\begin{figure}[!h]
		\begin{center}
		        \includegraphics[width=0.6\textwidth]{finalFigures/figures/sim_u_trace} 
%			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_u_trace} 
			\caption{Representative traceplot of $\bm{u}$ parameters from simulation study in Section \ref{accuracy}.}\label{fig:sim_u_trace}
		\end{center}
	\end{figure}

@@

	\begin{figure}[h!]
		\begin{center} 
		\includegraphics[width=0.6\textwidth]{finalFigures/figures/sadinle_speed_plot_slides2} 
		%\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_speed_plot_slides2} 
			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations in simulation study in Appendix \ref{app:appendix-speed}, including hashing step for \texttt{fabl}, for increasing values of both $n_A$ and $n_B$. We see near quadratic growth in run-time for \texttt{BRL}, and near linear growth for \texttt{fabl}.}\label{fig:app-speed1}
		\end{center}
	\end{figure}

	\begin{figure}[h!]
		\begin{center}
		 \includegraphics[width=0.6\textwidth]{finalFigures/figures/speed_plot_fixed_nB_slides2} 
		% \includegraphics[width=0.6\textwidth]{../notes/figures/speed_plot_fixed_nB_slides2} 
			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations in simulation study in Appendix \ref{app:appendix-speed}, including hashing step for \texttt{fabl}, with increasing $n_A$ and $n_B$ fixed at 500. We see linear growth in run-time for \texttt{BRL}, and near constant run-time for \texttt{fabl}.}\label{fig:app-speed2}
		\end{center}
	\end{figure}

@@

	\begin{figure}[!h]
		\begin{center}
		         \includegraphics[width=0.6\textwidth]{finalFigures/el_salvador/overlap_trace} 
%			\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/overlap_trace} 
			\caption{Traceplot for number of matches found across data files in El Salvador case study.} \label{fig:overlap_trace}
		\end{center}
	\end{figure}

	\begin{figure}[!h]
		\begin{center}
		         \includegraphics[width=0.6\textwidth]{finalFigures/el_salvador/m_trace} 
%			\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/m_trace} 
			\caption{Traceplot for $\bm{m}$ parameter in El Salvador case study.} 
			\label{fig:m_trace}
		\end{center}
	\end{figure}

	\begin{figure}[!h]
		\begin{center}
		        \includegraphics[width=0.6\textwidth]{finalFigures/el_salvador/u_trace} 
%			\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/u_trace} 
			\caption{Traceplot for $\bm{u}$ parameter in El Salvador case study.} 
			\label{fig:u_trace}
		\end{center}
	\end{figure}
\end{document}

>>>>

@@

	\begin{figure}[t]
		\begin{center}
%		\includegraphics[width=0.7\textwidth]{finalFigures/figures/sadinle_speed_plot2}  
	 \includegraphics[width=0.7\textwidth]{../notes/figures/sadinle_speed_plot2} 
			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations, including the hashing step for \texttt{fabl}, for increasing values of both $n_A$ and $n_B$, as described in Section \ref{speed}. We see near quadratic growth in run-time for \texttt{BRL}, and near linear growth for \texttt{fabl}.}\label{fig:speed1}
		\end{center}
	\end{figure}

@@

	\begin{figure}[h!]
		\begin{center} 
%		\includegraphics[width=0.7\textwidth]{finalFigures/figures/speed_plot_fixed_nB_slides} 
		\includegraphics[width=0.7\textwidth]{../notes/figures/speed_plot_fixed_nB_slides} 
			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations, including hashing step for \texttt{fabl}, with $n_B$ fixed at 500, as described in Section \ref{speed}. We see near linear growth in run-time for \texttt{BRL}, and near constant run-time for \texttt{fabl}.}\label{fig:speed2}
		\end{center}
	\end{figure}

@@

	\begin{figure}[t]
		\begin{center}
%		\includegraphics[width=0.7\textwidth]{finalFigures/figures/sadinle_sim_plot2} 
			\includegraphics[width=0.7\textwidth]{../notes/figures/sadinle_sim_plot2} 
			\caption{Posterior means and credible intervals for accuracy metrics under the replication of simulation study from \cite{sadinle_bayesian_2017}. For each level of overlap and each level of error, we have 100 paired sets of 500 records. Thus this table summarizes results for 900 data files. We see comparable performance for all levels of error and overlap.}
			\label{fig:sadinle_simulation}
		\end{center}
	\end{figure}

@@

\begin{figure}
	\begin{minipage}[c]{0.4\linewidth}
		\begin{center}
%		\includegraphics[width=\linewidth]{finalFigures/SEI_sensitivity/Z_plot}
		\includegraphics[width=\linewidth]{../SEI_sensitivity/Z_plot}
		\caption{Distinct values of $\hat{Z}$ in Section \ref{SEI-sensitivity} simulation.}
		\label{fig:SEI_Z}
		\end{center}
	\end{minipage}
	\hfill
	\begin{minipage}[c]{0.5\linewidth}
		\begin{center}
		\includegraphics[width=\linewidth]{finalFigures/SEI_sensitivity/eval_plot} 
%	\includegraphics[width=\linewidth]{../SEI_sensitivity/eval_plot} 
		\caption{Means and 95\% credible intervals for recall and precision in Section \ref{SEI-sensitivity} simulation.}
		\label{fig:SEI_eval}
	\end{center}
	\end{minipage}%
\end{figure}
	\section{Case Studies}
	\label{sec:case-studies}

@@

	\begin{figure}[t]
		\begin{center}
%		         \includegraphics[width=0.6\textwidth]{finalFigures/el_salvador/overlap_distribution_smallP_bayes}
	\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/overlap_distribution_smallP_bayes}
			\caption{Posterior distribution and Bayes estimate of overlap across the two files. We note they are quite similar under both methods.}
			\label{fig:overlap-plot}
		\end{center}
	\end{figure}

	\begin{figure}[t]
		\begin{center}
%		         \includegraphics[width=0.6\textwidth]{finalFigures/el_salvador/m_posterior_smallP} 
                  	\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/m_posterior_smallP} 
			\caption{Posterior estimates of $\bm{m}$ parameters with 95\% credible intervals for the El Salvador case study. They are quite similar across the two methods.}\label{fig:m-and-u}
			\label{fig:m-and-u}
		\end{center}
	\end{figure}

@@

	\begin{figure}[h]
		\begin{center}
%		        \includegraphics[width=0.6\textwidth]{finalFigures/nltcs/overlap_posterior4}
 		\includegraphics[width=0.6\textwidth]{../notes/figures/nltcs/overlap_posterior4}
			\caption{Posterior distribution and Bayes estimate of overlap across years 1982 and 1989 of NLTCS data.}
			\label{fig:nltcs-overlap-plot}
		\end{center}
	\end{figure}

@@

\begin{figure}[t]
	\begin{center}
%	        \includegraphics[width=0.6\textwidth]{finalFigures/figures/sadinle_sim_plot_partial_DR} 
		\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot_partial_DR} 
		\caption{Negative predictive value (NPV), positive predictive value (PPV), and decision rate (DR) on data files in the simulation in Appendix \ref{partial}. We see poorer performance for \texttt{fabl} only in situations with high overlap.}
		\label{fig:sadinle_simulation_partial}
	\end{center}
\end{figure}

@@

	\begin{figure}[!h]
		\begin{center}
%		        \includegraphics[width=0.6\textwidth]{finalFigures/figures/sim_overlap_trace} 
			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_overlap_trace} 
			\caption{Representative traceplot of overlap between files from simulation study in Section \ref{accuracy}.}\label{fig:sim_overlap_trace}
		\end{center}
	\end{figure}

	\begin{figure}[!h]
		\begin{center}
%		         \includegraphics[width=0.6\textwidth]{finalFigures/figures/sim_m_trace} 
		\includegraphics[width=0.6\textwidth]{../notes/figures/sim_m_trace} 
			\caption{Representative traceplot of $\bm{m}$ parameter from simulation study in Section \ref{accuracy}.}\label{fig:sim_m_trace}
		\end{center}
	\end{figure}

	\begin{figure}[!h]
		\begin{center}
%		        \includegraphics[width=0.6\textwidth]{finalFigures/figures/sim_u_trace} 
		\includegraphics[width=0.6\textwidth]{../notes/figures/sim_u_trace} 
			\caption{Representative traceplot of $\bm{u}$ parameters from simulation study in Section \ref{accuracy}.}\label{fig:sim_u_trace}
		\end{center}
	\end{figure}

@@

	\begin{figure}[h!]
		\begin{center} 
%		\includegraphics[width=0.6\textwidth]{finalFigures/figures/sadinle_speed_plot_slides2} 
		\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_speed_plot_slides2} 
			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations in simulation study in Appendix \ref{app:appendix-speed}, including hashing step for \texttt{fabl}, for increasing values of both $n_A$ and $n_B$. We see near quadratic growth in run-time for \texttt{BRL}, and near linear growth for \texttt{fabl}.}\label{fig:app-speed1}
		\end{center}
	\end{figure}

	\begin{figure}[h!]
		\begin{center}
%		 \includegraphics[width=0.6\textwidth]{finalFigures/figures/speed_plot_fixed_nB_slides2} 
		 \includegraphics[width=0.6\textwidth]{../notes/figures/speed_plot_fixed_nB_slides2} 
			\caption{Run-time for \texttt{BRL} and \texttt{fabl} to run 1000 Gibbs iterations in simulation study in Appendix \ref{app:appendix-speed}, including hashing step for \texttt{fabl}, with increasing $n_A$ and $n_B$ fixed at 500. We see linear growth in run-time for \texttt{BRL}, and near constant run-time for \texttt{fabl}.}\label{fig:app-speed2}
		\end{center}
	\end{figure}

@@

	\begin{figure}[!h]
		\begin{center}
%		         \includegraphics[width=0.6\textwidth]{finalFigures/el_salvador/overlap_trace} 
		\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/overlap_trace} 
			\caption{Traceplot for number of matches found across data files in El Salvador case study.} \label{fig:overlap_trace}
		\end{center}
	\end{figure}

	\begin{figure}[!h]
		\begin{center}
%		         \includegraphics[width=0.6\textwidth]{finalFigures/el_salvador/m_trace} 
			\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/m_trace} 
			\caption{Traceplot for $\bm{m}$ parameter in El Salvador case study.} 
			\label{fig:m_trace}
		\end{center}
	\end{figure}

	\begin{figure}[!h]
		\begin{center}
%		        \includegraphics[width=0.6\textwidth]{finalFigures/el_salvador/u_trace} 
		\includegraphics[width=0.6\textwidth]{../notes/figures/el_salvador/u_trace} 
			\caption{Traceplot for $\bm{u}$ parameter in El Salvador case study.} 
			\label{fig:u_trace}
		\end{center}
	\end{figure}
\end{document}
